A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-11 paper/ms.tex
update ms

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to rotation
period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS full
frame image data.\footnote{Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 28 stars; for these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 and
2.5 TESS magnitudes of the target star.

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.  To avoid blending, we also only
focused on stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

% \clearpage
\acknowledgements
\raggedbottom

@@

The catalogs we included for which ages were not immediately available
were those of \citet{CottenSong2016}, \citet{Oh2017},
\citet{Zari2018}, \citet{Gagne2018b}, \citet{Gagne2018a},
\citet{Gagne2018c}, and \citet{Ujjwal2020}.  While in principle the
moving group members discussed by
\citet{Gagne2018b,Gagne2018a,Gagne2018c} and \citet{Ujjwal2020} have
easily associated ages, our SIMBAD cross-match did not retain the
moving group identifiers given by those studies, which should
therefore be recovered using tools such as BANYAN
$\Sigma$.\footnote{\url{http://www.exoplanetes.umontreal.ca/banyan/banyansigma.php}}.
We also included the SIMBAD object identifiers $\texttt{TT*}$,
$\texttt{Y*O}, $\texttt{Y*?}, $\texttt{TT?}$, and $\texttt{pMS*}$.
Finally, we  included every star in the NASA Exoplanet Archive
planetary system ($\texttt{ps}$) table that had a Gaia identifier
available \citep{NASAExoArchive_ps_20210506}.  If the age had finite
uncertainties, we also included it, since stellar ages determined
through the combination of isochrone-fitting and transit-derived
stellar densities typically have higher precision than from isochrones
alone.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by quartiles in the
    local slope of the light curve}.  
    Representative uncertainties for the black points (binned at 20
    minute intervals) are shown in the lower right of each panel.  A
    similar transit asymmetry to that shown in Figure~\ref{fig:lc}
    seems to be present in three of the four bins.
    \vspace{-0.5cm}
		\label{fig:phaseslope}
	}
\end{figure}

>>>>

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to rotation
period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS full
frame image data. 
We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 TESS magnitudes of the target star.

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.  
Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 28 of these stars; for these cases, we
simply adopted the Kepler rotation period.
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

\clearpage
\acknowledgements
\raggedbottom

@@

The catalogs we included for which ages were not immediately available
were those of \citet{CottenSong2016}, \citet{Oh2017},
\citet{Zari2018}, \citet{Gagne2018b}, \citet{Gagne2018a},
\citet{Gagne2018c}, and \citet{Ujjwal2020}.  While in principle the
moving group members discussed by
\citet{Gagne2018b,Gagne2018a,Gagne2018c} and \citet{Ujjwal2020} have
easily associated ages, our SIMBAD cross-match did not retain the
moving group identifiers given by those studies, which should
therefore be recovered using tools such as BANYAN
$\Sigma$ \citep{Gagne2018a}.
We also included the SIMBAD object identifiers $\texttt{TT*}$,
$\texttt{Y*O}, $\texttt{Y*?}, $\texttt{TT?}$, and $\texttt{pMS*}$.
Finally, we  included every star in the NASA Exoplanet Archive
planetary system ($\texttt{ps}$) table that had a Gaia identifier
available \citep{NASAExoArchive_ps_20210506}.  If the age had finite
uncertainties, we also included it, since stellar ages determined
through the combination of isochrone-fitting and transit-derived
stellar densities typically have higher precision than from isochrones
alone.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by quartiles in the
    local slope of the light curve}.  
    Representative uncertainties for the black points (binned at 20
    minute intervals) are shown in the lower right of each panel.  A
    similar transit asymmetry to that shown in Figure~\ref{fig:lc}
    seems to be present in three of the four bins.
		\label{fig:phaseslope}
	}
\end{figure}
